Pre-trained encoders for dialogue: The case of laughter

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Caption for the results by DA groups

\section{Data}\label{sec:data}
We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} we cluster into a smaller set of 42 tags.
AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.

@@

@@

% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

@@

  \end{tabular}
  \caption{Comparison of macro-average F1 and micro-average accuracy depending on using laughter on the training phase. }
  \label{table:laughter-total-acc}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{@{}llcc@{}}
    \toprule
    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
  \end{tabular}
  \caption{Comparison of models depending on using laughter on the training phase. }
  \label{table:laughter-group-acc}
\end{table}

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
  \bottomrule
\end{tabular}
  \caption{Macro-average F1 and micro-average accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
  \label{table:exp2}
\end{table}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and micro-average accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}

>>>>

\section{Data}\label{sec:data}
We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.

@@

\paragraph{Preprocesing}
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

We make an effort to normalize transcription conventions across SWDA and AMI.
We remove disfluency annotations and slashes from the end of utterances in SWDA.
In both corpora, acronyms are tokenized as individual letters. 
All utterances are lower-cased.

Utterances are tokenized using BERT's word piece tokenizer with a vocabulary of 30,000.
We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.

@@

@@

  \end{tabular}
  \caption{Comparison of macro-average F1 and accuracy depending on using laughter on the training phase. }
  \label{table:laughter-total-acc}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{@{}llcc@{}}
    \toprule
    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
  \end{tabular}
  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
  \label{table:laughter-group-acc}
\end{table}

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
  \bottomrule
\end{tabular}
  \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
  \label{table:exp2}
\end{table}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lrrrr@{}}
\toprule
           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
\end{tabular}
  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
  \label{table:exp3}
\end{table}
